    \begin{longtable}[c]{lp{8cm}}
    \caption{Variable description of the real world application \label{tab:var_descr}}\\    %%%%<===
    \\[-1.8ex]\hline 
    \hline \\[-1.8ex] 
    Variable Name 	&	Description	\\ 
    \hline \\[-1.8ex] 
        age	&	age in. years in 2020	\\
        waist circ.	&	waist circumference in cm	\\
        height	&	standing in height in cm 	\\
        first illn.	&	age at which illness first occurred 	\\
        first surg. 	&	age at which operation was done first	\\
        pulse rate	&	pulse rate measured in bpm 	\\
        deprev. idx	&	Townsend deprivation index at recruitment	\\
        dur. walks	&	duration of walks in minutes per day	\\
        dur. mod. act. 	&	duration of moderate activity in minutes per day	\\
        dbp	&	diastolic blood pressure in mmHg	\\
        sbp	&	systolic blood pressure in mmHg	\\
        BMI	&	in kg/m2	\\
        weigth	&	in kg	\\
        b.f. perc.	&	body fat percentage in \%	\\
        walking	&	number of days per week walked 10+ minutes 	\\
        mod. phys. act.	&	number of days per week of moderate physical activity  10+ minutes 	\\
        vig. phys. act.	&	number of days per week of vigorous physical activity 10+ minutes 	\\
        cheese	&	answer to ``How often do you eat cheese per week?" 	\\
        stair climb.	&	answer to "At home, during the last 4 weeks, about how many times a DAY do you climb a flight of stairs? (approx 10 steps)" 	\\
        curr. smoking	&	categorial, "Do you smoke tobacco now?" (yes, no, occasionally)	\\
        past smoking	&	categorial, "How often did you smoke tobacco?" (never, once/twice, occasionally, on most days)	\\
        diet var.	&	categorial, "Does your diet change?" (never, sometimes, often)	\\
        alc. freq.	&	categorial, "How often do you drink alcohol?" (never, special occasions only, 1-3 per month, 1-2 per week, 3-4 per week, almost daily)	\\
        alc. var.	&	categorial, "Compared to 10 years ago, do you drink?" (more, about the same, less)	\\
        sex	&	binary indicator with 0=female, 1=male	\\
        hypertension	&	hypertension, binary indicator with 0=no, 1=yes	\\
        angina	&	angina, binary indicator with 0=no, 1=yes	\\
        heart attack	&	heart attack, binary indicator with 0=no, 1=yes	\\
        stroke	&	stroke, binary indicator with 0=no, 1=yes	\\
        dvt	&	deep venous thrombosis, binary indicator with 0=no, 1=yes	\\
        asthma	&	asthma, binary indicator with 0=no, 1=yes	\\
        chr. bronch.	&	emphysema/chronic bronchitis,  binary indicator with 0=no, 1=yes	\\
        gord	&	gastro-oesophageal reflux/gastric reflux, binary indicator with 0=no, 1=yes	\\
        ibs	&	irritable bowel syndrome, binary indicator with 0=no, 1=yes	\\
        gall stones	&	cholelithiasis/gall stones, binary indicator with 0=no, 1=yes	\\
        kidn./bladder stone 	&	kidney stone/ureter stone/bladder stone, binary indicator with 0=no, 1=yes	\\
        diabetes	&	diabetes, binary indicator with 0=no, 1=yes	\\
        diabtes 2	&	type 2 diabetes, binary indicator with 0=no, 1=yes	\\
        myxoedema	&	hypothyroidism/myxoedema, binary indicator with 0=no, 1=yes	\\
        migraine	&	migraine, binary indicator with 0=no, 1=yes	\\
        glaucoma	&	glaucoma, binary indicator with 0=no, 1=yes	\\
        cataract	&	cataract, binary indicator with 0=no, 1=yes	\\
        depression	&	depression, binary indicator with 0=no, 1=yes	\\
        panic attacks	&	anxiety/panic attacks, binary indicator with 0=no, 1=yes	\\
        back probl. 	&	back problems, binary indicator with 0=no, 1=yes	\\
        osteoporosis	&	osteoporosis, binary indicator with 0=no, 1=yes	\\
        spine arthr.	&	spine arthritis/spondylitis, binary indicator with 0=no, 1=yes	\\
        slipped disc	&	prolapsed disc/slipped disc, binary indicator with 0=no, 1=yes	\\
        anaemia 	&	iron deficiency anaemia, binary indicator with 0=no, 1=yes	\\
        ut. fibroids	&	uterine fibroids, binary indicator with 0=no, 1=yes	\\
        allerg. rhinitis	&	heyfever/allergic rhinitis, binary indicator with 0=no, 1=yes	\\
        enlarged prost.	&	enlarged prostate, binary indicator with 0=no, 1=yes	\\
        pneumonia	&	pneumonia, binary indicator with 0=no, 1=yes	\\
        endometr.	&	endometriosis, binary indicator with 0=no, 1=yes	\\
        ear disor.	&	ear/vestibular disorder, binary indicator with 0=no, 1=yes	\\
        headaches	&	headaches (not migraine), binary indicator with 0=no, 1=yes	\\
        ecz./dermat.	&	eczema/dermatitis, binary indicator with 0=no, 1=yes	\\
        psoriasis	&	psoriasis, binary indicator with 0=no, 1=yes	\\
        div. disease	&	diverticular disease/diverticulitis, binary indicator with 0=no, 1=yes	\\
        osteoarthr.	&	osteoarthritis, binary indicator with 0=no, 1=yes	\\
        gout	&	gout, binary indicator with 0=no, 1=yes	\\
        high chol.	&	high cholesterol, binary indicator with 0=no, 1=yes	\\
        hiat. hern.	&	hiatus hernia, binary indicator with 0=no, 1=yes	\\
        sciatica	&	sciatica, binary indicator with 0=no, 1=yes	\\
        appendic.	&	appendicitis, binary indicator with 0=no, 1=yes	\\
        back pain	&	back pain, binary indicator with 0=no, 1=yes	\\
        arthritis	&	arthritis (nos), binary indicator with 0=no, 1=yes	\\
        measles	&	measles/morbillivirus, binary indicator with 0=no, 1=yes	\\
        chickpox	&	chickenpox, binary indicator with 0=no, 1=yes	\\
        tonsillitis	&	tonsillitis, binary indicator with 0=no, 1=yes	\\
        ptca	&	coronary angioplasty (ptca)+/-stent, binary indicator with 0=no, 1=yes	\\
        ear surg.	&	ear surgery, binary indicator with 0=no, 1=yes	\\
        sinus surg.	&	nasal/sinus,nose surgery, binary indicator with 0=no, 1=yes	\\
        vasectomy	&	vasectomy, binary indicator with 0=no, 1=yes	\\
        soft tiss. surg.	&	mucsle/soft tissue surgery, binary indicator with 0=no, 1=yes	\\
        hip repl.	&	hip replacement/revision, binary indicator with 0=no, 1=yes	\\
        knee repl.	&	knee replacement/revision, binary indicator with 0=no, 1=yes	\\
        spine surg.	&	spine or back surgery, binary indicator with 0=no, 1=yes	\\
        bil. ooph.	&	bilateral oophorectomy, binary indicator with 0=no, 1=yes	\\
        hysterect.	&	hysterectomy, binary indicator with 0=no, 1=yes	\\
        steril.	&	sterilisation, binary indicator with 0=no, 1=yes	\\
        lumpect.	&	lumpectomy, binary indicator with 0=no, 1=yes	\\
        ing. hernia rep.	&	inguinal/femoral hernia repair, binary indicator with 0=no, 1=yes	\\
        umb. hernia rep.	&	umbilical hernia repair, binary indicator with 0=no, 1=yes	\\
        cataract extr.	&	catarct extraction/lens implant, binary indicator with 0=no, 1=yes	\\
        red./fix. bone frac.	&	reduction or fixationof bone fracture, binary indicator with 0=no, 1=yes	\\
         cholecystect. 	&	cholecystectomy/gall bladder removal, binary indicator with 0=no, 1=yes	\\
        appendicect.	&	appendicectomy, binary indicator with 0=no, 1=yes	\\
        c-sec.	&	caesarian section, binary indicator with 0=no, 1=yes	\\
        tonsillest.	&	tonsillectomy, binary indicator with 0=no, 1=yes	\\
        var. vein surg.	&	varicose vein surgery, binary indicator with 0=no, 1=yes	\\
        wisd. teeth surg.	&	wisdom teeth surgery, binary indicator with 0=no, 1=yes	\\
        piles surg.	&	haemorroidectomy/piles surgery/banding of piles, binary indicator with 0=no, 1=yes	\\
        male circ.	&	male circumcision, binary indicator with 0=no, 1=yes	\\
        squint corr.	&	squint correction, binary indicator with 0=no, 1=yes	\\
        arthrosc.	&	arthroscopy (nos), binary indicator with 0=no, 1=yes	\\
        foot surg.	&	foot surgery, binary indicator with 0=no, 1=yes	\\
        knee surg.	&	knee surgery (not replacement), binary indicator with 0=no, 1=yes	\\
        shoulder surg.	&	shoulder surgery, binary indicator with 0=no, 1=yes	\\
        car. tunn. surg.	&	carpal tunnel surgery, binary indicator with 0=no, 1=yes	\\
        valg. surg.	&	bunion/hallus valgus surgery, binary indicator with 0=no, 1=yes	\\
        rem. mole	&	removal of mole/skin lesion, binary indicator with 0=no, 1=yes	\\
        ov. cyst. rem.	&	ovarian cyst removal/surgery, binary indicator with 0=no, 1=yes	\\
        d+c	&	dilatation and curettage, binary indicator with 0=no, 1=yes	\\
        cone biops.	&	cone biopsy, binary indicator with 0=no, 1=yes	\\
        endosc.	&	endoscopy/gastroscopy, binary indicator with 0=no, 1=yes	\\
        colonosc.	&	colonoscopy/sigmoidoscopy, binary indicator with 0=no, 1=yes	\\
        laparosc.	&	laparoscopy, binary indicator with 0=no, 1=yes	\\
        rhinoplast.	&	rhinoplasty/nose surgery, binary indicator with 0=no, 1=yes	\\
        tonsil surg.	&	tonsillectomy/tonsil surgery, binary indicator with 0=no, 1=yes	\\
        ing. hern. rep.	&	inguinal hernia repair, binary indicator with 0=no, 1=yes	\\
        illn. ind. diet	&	Major dietary changes in the last 5 years because of illness, binary indicator with 0=no, 1=yes	\\
        diet change	&	Major dietary changes in the last 5 years  because of other reason, binary indicator with 0=no, 1=yes	\\
        ethn. Mixed	&	Ethnicity - mixed, binary indicator with 0=no, 1=yes	\\
        ethn. Asian	&	Ethnicity - Asian, binary indicator with 0=no, 1=yes	\\
        ethn. Black	&	Ethnicity - Black, binary indicator with 0=no, 1=yes	\\
        no eggs	&	Never eat eggs or foods containing eggs, binary indicator with 0=no, 1=yes	\\
        no dairy	&	Never dairy products, binary indicator with 0=no, 1=yes	\\
        no wheat	&	Never eat wheat, binary indicator with 0=no, 1=yes	\\
        no sugar	&	Never eat sugar or foods/drinks containing sugar, binary indicator with 0=no, 1=yes	\\
        walk. f. pleas.	&	Types of physical activity in last 4 weeks - walking for pleasure, binary indicator with 0=no, 1=yes	\\
        exercises	&	Types of physical activity in last 4 weeks - other exercises (swimming, bowling etc.), binary indicator with 0=no, 1=yes	\\
        stren. Sports	&	Types of physical activity in last 4 weeks -  strenuous sports, binary indicator with 0=no, 1=yes	\\
        Covid-19 severity	&	Covid-19 severity, binary indicator with 0=mild outcome and 1=severe outcome	\\
    \hline
\end{longtable}
